Blocking-resistant communication\\through domain fronting

### 2014-07-29 docs/meek.tex
Revisions on packet length.

% Advantage is that we are probably proxying web traffic.

The censor cannot sniff the content of communications or infer the usage of meek 
from packet \emph{data}, 
since the communication is encrypted inside the TLS session, and we have devoted large efforts 
in hiding TLS handshake fingerprints. However, it is still possible that the censor can detect 
the existence of meek according to the \emph{meta-data}, i.e. traffic characteristics. 
In this section we study a collection of traffic characteristics and evaluate their possibilities of becoming
the censor's interest. Specifically, we consider three characteristics: 1) payload length of
TCP packets, 2) number of concurrent HTTPS connections, 3) HTTPS connection lifetime.

To collect the traffic trace of meek, we browses the Alexa top 500 websites sequentially using 
the Tor Browser Bundle and dump the traffic trace from the network interface. We ensured only
the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983~megabytes in total. 
We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
only has packet headers, we cannot extract the domain information. However, the \texttt{TXT} DNS
records of the domain \texttt{\_netblocks.google.com} shows the IP address blocks that belongs to
Google. Therefore, we determine whether a flow is from or to Google by examining the address in the 
IP header. We only interested in the Google traffic only, because the censor who wants to defeat meek
will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
Google trace is 312~megabytes.

\begin{figure*}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-google-cdf.png}
\caption{Normal Google Traffic}
\label{fig:len:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-tbb-cdf.png}
\caption{Traffic Using meek}
\label{fig:len:meek}
\end{subfigure}

\caption{TCP packet payload size distribution}
\label{fig:len}
\end{figure*}

\paragraph{TCP payload length}
Figure ~\ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
packets. Figure ~\ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
of small-sized packets. However, in the meek's traffic shown in Figure ~\ref{fig:len:meek}, most packets
are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
distribution. Therefore, meek provides traffic shaping without additional efforts.

@@

\paragraph{Concurrent connections}
Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

@@

\paragraph{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

@@

\paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
distinguishing meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what is the model of normal traffic, which is an open problem. However, 
the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
easy to defend against.

@@

% Censors that know no bounds: China on Google, Egypt.

>>>>

One of our goals in developing meek is to force
the censor to use relatively expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe meek as described is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication like
the packet length distribution and interpacket timing,
or injecting traffic at the risk of causing collateral damage.
In this section we provide a preliminary analysis
of meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
and mostly orthogonal to meek's main idea, domain fronting.
It may be that the problem is
best solved by a modular component not
specifically designed for meek.

% Advantage is that we are probably proxying web traffic.
As meek is based on HTTPS,
we compare traffic traces of meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using meek,
with a firewall in place so that no extraneous traffic was included.
The browser used was Tor Browser,
with the browser camouflage for meek described in Section~\ref{sec:browserextension},
using Google App Engine as the intermediate web service.
The meek trace is 687~megabytes in all.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
originating at Lawrence Berkeley National Laboratory (LBL).
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The original IP addresses were replaced with a counter.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and meek running on App Engine, fronted through www.google.com.
The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
A few similarities are noticeable:
roughly 37\% of packets have no payload; these are mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
% Other peaks near the max are probably near 1400, TLS maximum record size.
The meek trace is missing a small peak of small packets
present in the LBL trace.
In its place, there are minor peaks at fairly distinct values,
probably a reflection of Tor's fixed cell size
and the fixed overhead of an encrypted HTTP header added
to each transmission by meek.
% Maybe mention apparent residue of a doubling of the three peaks at around 750.
meek's trace is tends more overall to larger packets.

@@

\subsection{Concurrent connections}
Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

@@

\subsection{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

@@

\subsection{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
distinguishing meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what is the model of normal traffic, which is an open problem. However, 
the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
easy to defend against.

@@

% Censors that know no bounds: China on Google, Egypt, Pakistan with YouTube.
